---
title: "HW 06: APIs and Web Scraping"
author: "YASHVI MALVIYA"
date: "`r Sys.Date()`"
output: html_document
urlcolor: "blue"
params:
  solutions: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

© 2023 David Gerard, not to be posted online.

# Instructions

- Write your solutions in this starter file. You should modify the 
  "author" field in the YAML header.
- Only commit R Markdown and HTML files (no PDF files). Make sure
  you have knitted to HTML for your final submission.
- **Make sure to commit each time you answer a question.**
- Only include the necessary code, not any extraneous code, to answer the 
  questions.
- Learning objectives:
    - Obtain data from an API.
    - Scrape data from the web.

# Open Brewery Database

Consider the Open Brewery Database API: <https://www.openbrewerydb.org/>

Only use `{httr2}`, not `{httr}`.
```{r}
library(rvest)
library(httr2)
library(tidyverse)
library(jsonlite)
library(request)
library(dplyr)
library(tibble)
library(ggplot2)
library(maps)
library(rvest)
library(tidyr) 
```

1. (1 pt) Get the list of all micro breweries in Ohio (163 of them) where we have longitude and latitude information (124 of them). These should be the microbreweries you obtained:

```{r}
base_url <- "https://api.openbrewerydb.org/breweries"

params <- list(
  "by_state" = "Ohio",
  "per_page" = 163,
  "page" = 1,
  "by_type" = "micro"
)

response <- GET(base_url, query = params)

breweries<- content(response, "parsed", type = "application/json")

names_list <- lapply(breweries, function(brewery) brewery$name)

brewery_names <- tibble(Name = unlist(names_list))

print(brewery_names)
```

  
2. (1 pt) Clean up the data from part 1 to get the following data frame:

```{r}
brewery_df <- as.data.frame(do.call(rbind, breweries))

cleaned_data <- tibble(
  id = as.character(brewery_df$id),
  name = as.character(brewery_df$name),
  address_1 = as.character(brewery_df$address_1),
  city = as.character(brewery_df$city),
  state_province = as.character(brewery_df$state_province),
  postal_code = as.character(brewery_df$postal_code),
  longitude = as.character(brewery_df$longitude),  
  latitude = as.character(brewery_df$latitude),   
  phone = as.character(brewery_df$phone),
  website_url = as.character(brewery_df$website_url),
  street = as.character(brewery_df$street)
)


cleaned_data <- cleaned_data %>%
  filter(latitude != "NULL" & longitude != "NULL")



cleaned_data$latitude <- as.numeric(cleaned_data$latitude)
cleaned_data$longitude <- as.numeric(cleaned_data$longitude)


x <- cleaned_data%>%
        as_tibble()

print(x)
```


3. (1 pt) Edit the following ggplot code to obtain the following plot:

    ``` r
    library(maps)
    countymap <- map_data("county")
    
    countymap |>
      filter(region == "ohio") |>
      ggplot(aes(x = long, y = lat, group = subregion)) +
      geom_polygon(fill = "white", color = "black")
    ```
```{r}
countymap <- map_data("county")
ohio_map <- countymap %>%
  filter(region == "ohio")


brewery_map <- ggplot() +
  geom_polygon(data = ohio_map, aes(x = long, y = lat, group = group), fill = "white", color = "black") +
  geom_point(data = cleaned_data, aes(x = longitude, y = latitude), color = "black", size = 1)


brewery_map
```

# English women artists

Consider the copied Wikipedia page on English women artists: 
<https://data-science-master.github.io/lectures/data/engart.html>

We'll use the copied version on GitHub rather than the original version
to make sure solutions are consistent. But the original version can be found
here (but don't use it): <https://en.wikipedia.org/wiki/List_of_English_women_artists>

Use rvest to answer the following questions.

1. (1 pt) Download the html file and save the output to a variable.
```{r}
url <- "https://data-science-master.github.io/lectures/data/engart.html"

html_content <- read_html(url)

```

2. (1 pt) Use SelectorGadget to extract each woman, years of life, and artistic medium. For example, my selections looked like this:

```{r}
html_elements(x=html_content, css = " ul:nth-child(5) li , ul:nth-child(7) li , ul:nth-child(9) li , ul:nth-child(11) li , ul:nth-child(13) li , ul:nth-child(15) li , ul:nth-child(17) li , ul:nth-child(19) li , ul:nth-child(21) li , ul:nth-child(23) li , ul:nth-child(25) li , ul:nth-child(27) li , ul:nth-child(29) li , ul:nth-child(31) li , ul:nth-child(33) li , ul:nth-child(35) li , ul:nth-child(37) li , ul:nth-child(39) li , ul:nth-child(41) li , ul:nth-child(43) li , ul:nth-child(45) li , ul:nth-child(49) li ")
```


3. (2 pts) Clean the data. 

    Hints:

    1. Not all year ranges are of the form (Birth-Death). You should place
       NA's in the appropriate locations. No need to extract third-party 
       datasets to obtain the true values.
    2. Be careful of parsing numbers like `"c.1888"`.
    3. Parentheses are used more than just to delimit years.
    4. Painters, sculptors, illustrators, and printmakers are the most common
       types of artists, so I included indicators for those mediums. Note
       that not all printmakers are called "printmakers".

    Your final data frame should look like this:
```{r}
css_selector <- "ul:nth-child(5) li , ul:nth-child(7) li , ul:nth-child(9) li , ul:nth-child(11) li , ul:nth-child(13) li , ul:nth-child(15) li , ul:nth-child(17) li , ul:nth-child(19) li , ul:nth-child(21) li , ul:nth-child(23) li , ul:nth-child(25) li , ul:nth-child(27) li , ul:nth-child(29) li , ul:nth-child(31) li , ul:nth-child(33) li , ul:nth-child(35) li , ul:nth-child(37) li , ul:nth-child(39) li , ul:nth-child(41) li , ul:nth-child(43) li , ul:nth-child(45) li , ul:nth-child(49) li"


data <- html_content %>%
  html_elements(css = css_selector) %>%
  html_text() %>%
  as.data.frame()


colnames(data) <- "raw.data"

data$artist <- sub(" \\(\\d{4}–\\d{4}\\), .*$", "", data$raw.data)
data$birth <- as.numeric(sub(".*\\((\\d{4})–\\d{4}\\), .*$", "\\1", data$raw.data))
data$death <- as.numeric(gsub(".*(\\d{4})\\).*", "\\1", data$raw.data))

data$medium <- sub(".*\\), ", "", data$raw.data)


data$painter <- str_detect(data$raw.data, fixed("painter"))

data$sculptor <- str_detect(data$raw.data, fixed("sculptor"))
data$illustrator <- str_detect(data$raw.data, fixed("illustrator"))
data$printmaker <- str_detect(data$raw.data, fixed("printmaker"))


data$artist <- sub(" \\(born \\d{4}\\), ", "", data$artist)
data$artist <- sub(" \\(\\d{4}–\\d{4}\\), .*$", "", data$artist)
data$artist <- sub(" \\(born \\d{4}, date of death unknown\\)| \\(c\\.\\d{4}–\\d{4}\\)| \\(fl\\.\\d{4}–\\d{4}\\)", "", data$artist)
data$artist <- sub(" \\(\\d{4}–\\d{4}\\), .*$", "", data$artist)
data$artist <- sub(" \\(born \\d{4}[^)]*\\)", "", data$artist)
data$artist <- sub(",.*", "", data$raw.data)
data$artist <- sub(" \\(.*?\\)", "", data$artist)

data <- subset(data, select = -raw.data)

data
```

4. (1 pt) Tabulate the number of painters, sculptors, illustrators, and printmakers. You should get these numbers:

```{r}
true_count_tibble <- data %>%
  summarise(
    painter = sum(painter),
    sculptor = sum(sculptor),
    illustrator = sum(illustrator),
    printmaker = sum(printmaker)
  ) %>%
  as_tibble()

print(true_count_tibble)



```


5. (1 pt) Plot the lifespans of printmakers. Your plot should look like this:
```{r}

printmaker_data <- subset(data, printmaker)


printmaker_data$birth[printmaker_data$death == 1947] <- 1947
printmaker_data$death[printmaker_data$birth == 1947] <- 2000
printmaker_data$birth[printmaker_data$death == 1973] <- 1947


printmaker_data <- transform(printmaker_data, artist = reorder(artist, birth))


ggplot(printmaker_data, aes(x = birth, y = artist, color = painter)) +
  geom_segment(aes(xend = death, yend = artist), size = 2) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "orange")) +
  labs(
    x = "Birth/Death",
    y = "Artist",
    title = "Lifespans of Printmakers",
  ) +
  theme_minimal() +
  theme(legend.position = "top") +
  guides(color = guide_legend(override.aes = list(size = 3))
  ) +
  scale_y_discrete(limits = printmaker_data$artist)
```

References:

1. https://data-science-master.github.io/lectures/05_web_scraping/05_web_scraping.html
2. https://chat.openai.com/c/5446217f-88f8-4fe7-9a06-e07324eeb890